Component-Based mruby Platform for IoT Devices

### 2017-11-16 ipsj/paper.tex
Remove an unused section
Final version

\usepackage[dvipdfmx]{graphicx}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{color}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
The proposed framework can enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
In addition, this paper proposes two component-based functionality such as a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.

@@

%1
\section{Introduction}
\label{sec:Introduction}

@@

Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}, \cite{par:CBD}.
Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
Individual component diagrams enable the visualization of an entire system.
In addition, component-based systems are flexible with regard to extensibility and specification changes.
The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.

@@

For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
Therefore, applying scripting languages to embedded systems is difficult.
To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}, \cite{par:mrubyonTECS3}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.

@@

{\bf Contributions}: The proposed framework provides the following contributions.
\begin{enumerate}
\item {\bf Applicable to various devices:}
The proposed framework does not depend on RTOSs or hardware, it can be utilized in various devices.
mruby code is portable.
Therefore, it is possible to run the same program on different devices.

\item {\bf Improve configurability:}
Because TINET+TECS is a component-based system, its software can flexibly change as system configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
In addition, the use by TINET+TECS of individual component diagrams enables visualization of an entire system.

\item {\bf Thread-safe memory allocator:}
TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
Moreover, each thread can easily set own heap area.

\end{enumerate}

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model of the proposed framework and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

%2
\section{System Model}
\label{sec:System Model}

This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.

The following subsection explains TECS, mruby, and mruby on TECS framework.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
    \caption{System model of the proposed framework}
    \label{fig:SystemModel}
\end{figure}

\subsection{TECS}
\label{sec:TECS}

@@

In TECS, component deployment and composition are performed statically.
Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Fig.\ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\subsubsection{Component Description}
In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
% TECS code is written in CDL (component description language) file.
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees,
               [in] uint32_t speed_abs,
                [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
    \caption{Development flow using TECS}
    \label{fig:TECSFlow}
\end{figure}

@@

\subsection{mruby}
\label{sec:mruby}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mruby.pdf}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

\subsection{mruby on TECS}
\label{sec:mrubyonTECS}

@@

\subsubsection{System Model of mruby on TECS}
The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.

In this paper, TOPPERS/ASP3 \cite{par:ASP}, \cite{url:ASP} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mrubyonTECS.pdf}
\caption{System model of existing mruby on TECS}
\label{fig:mrubyonTECS}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mrubyTECSbridge.pdf}
\caption{mruby-TECS bridge}
\label{fig:mrubyTECSbridge}
\end{figure}

@@

%3
\section{Proposed Framework}
\label{sec:Proposed Framework}

@@

\subsection{TINET+TECS}
\label{sec:TINET+TECS}

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a real-time operating system (RTOS) developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
TINET has been released as an open-source tool.

To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports the following functions:

\begin{itemize}
    \item minimum copy frequency,
    \item elimination of dynamic memory control,
    \item asynchronous interfacing,
    \item error detailing per API.
\end{itemize}

@@

Fig.\ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
Users transmit and receive data using a Communication End Point (CEP), an interface that functions like a socket.
In the transmission process, headers are attached to the data body passed to the CEP at each protocol layer before the data are transmitted from the network device.
In the reception process, the headers of the data bodies received by the network device are analyzed at each protocol layer, and the data are then passed to the CEP.

@@

In TINET, the amount of data copying between each protocol layer is minimized.
In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
To solve this problem, TINET does pass the pointer of the data buffer between each protocol layer instead of performing data copying.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

The components of the TINET+TECS protocol stack are shown in Fig.\ref{fig:ComponentProtocolStack}.
Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and functionalities such as input and output functions are defined as respective components.
By using such small grain components, software visibility is improved.
The components of each protocol are described in the following.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of a protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

@@

{\bf Transport layer:}
tTCPCEP (tUDPCEP) and tREP are, respectively, CEP and REP components TCP (UDP).
For example, a server program supporting multiple clients can be developed by preparing multiple tTCPCEP components.
tTCPInput (tUDPInput) and tTCPOutput (tUDPOutput) are components for performing, respectively, receiving and sending processing in the transport layer.

@@

To utilize the protocol stack in the same manner in the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and an application.
The communication object component corresponds to a CEP or REP of the original TINET.
Application developers can utilize the TINET+TECS functionalities by generating and combining as many components as necessary.

The protocol stack of TINET+TECS supports the coexistence of multiple protocols.
Though its use of IPv6 and Point-to-Point Protocol (PPP) components, TINET+TECS can make IPv4 and IPv6 coexist and support PPP without modification of component implementation.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

\item {\it send} is another specifier for transferring data to a callee from a caller such as {\it in}.
The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
In the case of the {\it in} specifier, both allocating and deallocating of the data memory are performed in the caller.
By contrast, in the case of {\it send}, the caller allocates the data memory and the callee deallocates it.

@@

\item {\it receive} is another specifier for a caller receiving data from a callee such as {\it out}.
The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
In the case of {\it out}, the callee writes data in the memory allocated by a caller, whereas in the {\it receive} case, the callee allocates the data memory.
Deallocating of the memory is performed in the caller in both cases.
\end{itemize}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp, .., ..);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp, .., ..);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description of the nic driver (An example of send/receive)}
\label{src:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
    \vspace{-3mm} \caption{Dynamic connection}
    \vspace{-1mm} \label{fig:DynamicConnection}
\end{figure}

TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

>>>>

\usepackage[dvipdfmx]{graphicx}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{color}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\footnotesize\ttfamily},%
    identifierstyle={\footnotesize},%
    commentstyle={\scriptsize\itshape},%
    keywordstyle={\footnotesize},%\bfseries},%
    ndkeywordstyle={\footnotesize},%
    stringstyle={\footnotesize\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
The proposed framework enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
In addition, this paper proposes two component-based functionality such as a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.

@@

%1
\vspace{-1mm}
\section{Introduction}
\label{sec:Introduction}
\vspace{-1mm}

@@

Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic},\cite{par:CBD}.
Component-Based Development is a design technique that can be applied to reusable software development.
Verification of component-based systems has been extensively researched \cite{par:Blaming},\cite{par:Verification}.
Individual component diagrams enable the visualization of an entire system.
In addition, component-based systems are flexible with regard to extensibility and specification changes.
The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.

@@

For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
Therefore, applying scripting languages to embedded systems is difficult.
To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS},\cite{par:mrubyonTECS3}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby},\cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.

@@

{\bf Contributions}: The proposed framework provides the following contributions.

{\bf Applicable to various devices}
The proposed framework does not depend on RTOSs or hardware, it can be utilized in various devices.
mruby code is portable.
Therefore, it is possible to run the same program on different devices.

{\bf Improve configurability}
Because TINET+TECS is a component-based system, its software can flexibly change as system configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
In addition, the use of individual component diagrams enables visualization of an entire system.

{\bf Thread-safe memory allocator}
TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
Moreover, each thread can easily set own heap area.

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work} and Section \ref{sec:Conclusion} concludes this paper.

%2
\vspace{-1mm}
\section{System Model}
\label{sec:System Model}
\vspace{-1mm}

This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
The following subsection explains TECS, mruby, and mruby on TECS framework.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
    \vspace{-1mm} \caption{System model of the proposed framework}
    \vspace{-2mm} \label{fig:SystemModel}
\end{figure}

\vspace{-3mm}
\subsection{TECS}
\label{sec:TECS}
\vspace{-1mm}

@@

TECS statically performs component deployment and composition.
Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
    \vspace{-1mm} \caption{Component Diagram}
    \vspace{-2mm} \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Fig.\ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes and variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\subsubsection{Component Description}
In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    void initializePort( [in]int32_t type );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
};
\end{lstlisting}
\vspace{-2mm} \caption{Signature Description}
\vspace{-2mm} \label{signature}
\end{figure}
    \item[{\bf Celltype Description}]
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
\vspace{-2mm} \caption{Celltype Description}
\vspace{-2mm} \label{celltype}
\end{figure}
    \item[{\bf Build Description}]
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\vspace{-2mm} \caption{Build Description}
\vspace{-2mm} \label{build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
    \vspace{-1mm} \caption{Development flow using TECS}
    \vspace{-2mm} \label{fig:TECSFlow}
\end{figure}

@@

\vspace{-3mm}
\subsection{mruby}
\label{sec:mruby}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \vspace{-1mm} \caption{mruby/RiteVM mechanism}
    \vspace{-2mm} \label{fig:mruby}
\end{figure}

\vspace{-3mm}
\subsection{mruby on TECS}
\label{sec:mrubyonTECS}
\vspace{-1mm}

@@

\subsubsection{System Model of mruby on TECS}
% The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.
An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.

In this paper, TOPPERS/ASP3 \cite{par:ASP3},\cite{url:ASP3} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2},\cite{par:hr-tecs}.

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=6.5cm,clip]{figure/mrubyonTECS.pdf}
% \caption{System model of existing mruby on TECS}
% \label{fig:mrubyonTECS}
% \end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyTECSbridge.pdf}
\vspace{-1mm} \caption{mruby-TECS bridge}
\vspace{-2mm} \label{fig:mrubyTECSbridge}
\end{figure}

@@

%3
\vspace{-1mm}
\section{Proposed Framework}
\label{sec:Proposed Framework}
\vspace{-1mm}

@@

\vspace{-3mm}
\subsection{TINET+TECS}
\label{sec:TINET+TECS}
\vspace{-1mm}

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is an RTOS developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
TINET has been released as an open-source tool.
To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports the functions such as minimum copy frequency, elimination of dynamic memory control, asynchronous interfacing, error detailing per API.

@@

Fig.\ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
Users send and receive data using a Communication End Point (CEP), an interface that functions like a socket.
In the transmission process, headers are attached to the data body passed to the CEP at each protocol layer before the data are transmitted from the network device.
In the reception process, the headers of the data bodies received by the network device are analyzed at each protocol layer, and the data are then passed to the CEP.

@@

In TINET, the amount of data copying at each protocol layer is minimized.
In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
To solve this problem, TINET does pass the pointer of the data buffer between each protocol layer instead of data copying.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \vspace{-2mm} \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

The components of the TINET+TECS protocol stack are shown in Fig.\ref{fig:ComponentProtocolStack}.
Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and functionalities such as input/output functions are defined as respective components.
By using such small grain components, software visibility is improved.
The components of each protocol are described as follows.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \vspace{-1mm} \caption{Component diagram of a protocol stack}
    \vspace{-2mm} \label{fig:ComponentProtocolStack}
\end{figure}

@@

{\bf Transport layer:}
tTCPCEP (tUDPCEP) and tREP are, respectively, CEP and REP components.
For example, a server program supporting multiple clients can be developed by preparing multiple tTCPCEP components.
tTCPInput and tTCPOutput are components for performing, respectively, receiving and sending processing in the transport layer.

@@

To utilize the protocol stack in the same manner in the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and applications.
The communication object component corresponds to a CEP or REP of the original TINET.
Application developers can utilize TINET+TECS functionalities by generating and combining as many components as necessary.

TINET+TECS supports the coexistence of multiple protocols.
Though its use of IPv6 and Point-to-Point Protocol (PPP) components, TINET+TECS can make IPv4 and IPv6 coexist and support PPP without modification of component implementation.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/tMemoryAllocator.pdf}
    \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
    \vspace{-2mm} \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SendReceive.pdf}
    \vspace{-1mm} \caption{Differences between in/out and send/receive}
    \vspace{-2mm} \label{fig:SendReceive}
\end{figure}

@@

\item {\it send} is another specifier for transferring data to a callee from a caller.
The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
In the case of the {\it in} specifier, both allocating and deallocating of the data memory are performed in the caller.
By contrast, in the case of {\it send}, the caller allocates the data memory and the callee deallocates it.

@@

\item {\it receive} is another specifier for a caller receiving data from a callee.
The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
In the case of {\it out}, the callee writes data in the memory allocated by a caller, whereas in the {\it receive} case, the callee allocates the data memory.
Deallocating of the memory is performed in the caller in both cases.
\end{itemize}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp, .., ..);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp, .., ..);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
\vspace{-2mm} \label{src:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
    \vspace{-1mm} \caption{Dynamic connection}
    \vspace{-2mm} \label{fig:DynamicConnection}
\end{figure}

TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig.\ref{fig:DynamicConnection}) as a new functionality.
In Fig.\ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig.\ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
    \vspace{-2mm} \label{fig:DynamicConnectionUseCase}
\end{figure}
